---
title: "Unit 1 - 3 Review Starter"
author: "Not Me"
date: "Feb 23, 2023"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sites <- read_csv("data/sand_minerals.csv")
location_descriptions <- read_csv("data/location_descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility_hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sites)
names(sites)
```

There are 23 rows and 2 variables.
Each row corresponds to an individual mineral grain.


### Exercise 2

```{r inspect-other-data-frames}
glimpse(density)
glimpse(solubility_hardness)
glimpse(location_descriptions)
names(density)
names(solubility_hardness)
names(location_descriptions)
```
Density contains 3 rows and 2 columns; each row is a mineral density value for 3 minerals.
solubility_hardness contains 3 rows and 3 columns; each row is a hardness and solubility value for 3 minerals.
location_descriptions contains 10 rows and 2 columns; each row is a location description for 10 different mineral samples.

### Exercise 3

```{r join-mineral-properties}
sand_mineral_density <- sites %>% 
  left_join(density)
```

```{r}
sand_mineral_properties <- sand_mineral_density %>% 
  left_join(solubility_hardness)
```


### Exercise 4

```{r}
sand_mineral_properties %>% 
  count(location)

sand_mineral_properties %>% 
  group_by(location) %>% 
  summarize(count = n())
```


### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

## Part II - Data Visualization

`starwars` is already loaded within the `dplyr` package (within `tidyverse`)

### Exercise 7

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 8

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 9

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
